Cooperative Kernels: Safe Multitasking for Blocking Algorithms on GPUs

### 2016-11-11 write-ups/PLDI/paper.tex
Add line references for workstealing examples

\begin{lstlisting}
kernel work_stealing(global Task * pools) {
  while (more_work(pools)) {
    int pool_id = get_group_id();
    Task * t = pop_or_steal(pools, pool_id);
    if (t) {
      // task processing may create more work
      process_task(t, pools, pool_id);
    }
  }
}
\end{lstlisting}

@@

\myfiglong\ref{fig:workstealing} shows a simplified version of an OpenCL
kernel that uses a work stealing queue. All threads start their execution at the
function marked with the $\mathsf{kernel}$ keyword. They receive a
pointer to the task pools, which reside in global memory, and which
were initialized by the host program beforehand to contain the initial
tasks. Each thread can identify the workgroup it belongs to via the
function $\getgroupid()$.  Here the group id is stored into the
variable $\mathsf{pool\_id}$ (which is, by default, in private memory)
and used to access the relevant task pool. The
$\mathsf{pop\_or\_steal}$ function is called by all threads of a
workgroup.  Inside $\mathsf{pop\_or\_steal}$ only the thread with a local id equal to
$0$, also called the \emph{master thread} of the workgroup,
will try to pop a task
from the workgroup's pool, or steal a task from a different pool. The
master thread uses local memory inside $\mathsf{pop\_or\_steal}$ to
ensure that the returned value is valid for all threads of its
workgroup. If a task was obtained, then all threads of the workgroup
participate in the processing of the task via the
$\mathsf{process\_task}$ function.  Processing this task may lead to the creation of further
tasks, which the master thread will push to the workgroup's pool.

>>>>

\begin{lstlisting}
(*@\label{line:wksteal:kernelfunc}@*) kernel work_stealing(global Task * pools) {
  while (more_work(pools)) {
(*@\label{line:wksteal:getgroupid}@*)    int pool_id = get_group_id();
(*@\label{line:wksteal:poporsteal}@*)    Task * t = pop_or_steal(pools, pool_id);
    if (t) {
      // task processing may create more work
(*@\label{line:wksteal:processtask}@*)      process_task(t, pools, pool_id);
    }
  }
}
\end{lstlisting}

@@

\myfiglong\ref{fig:workstealing} shows a simplified version of an OpenCL
kernel that uses a work stealing queue. All threads start their
execution at the function marked with the $\mathsf{kernel}$ keyword
(line~\ref{line:wksteal:kernelfunc}). They receive a pointer to the task
pools, which reside in global memory, and which were initialized by the
host program beforehand to contain the initial tasks. Each thread can
identify the workgroup it belongs to via the function $\getgroupid()$
(line~\ref{line:wksteal:getgroupid}). Here the group id is stored into
the variable $\mathsf{pool\_id}$ (which is, by default, in private
memory) and used to access the relevant task pool. The
$\mathsf{pop\_or\_steal}$ function (line~\ref{line:wksteal:poporsteal})
is called by all threads of a workgroup.  Inside
$\mathsf{pop\_or\_steal}$ only the thread with a local id equal to $0$,
also called the \emph{master thread} of the workgroup, will try to pop a
task from the workgroup's pool, or steal a task from a different
pool. The master thread uses local memory inside
$\mathsf{pop\_or\_steal}$ to ensure that the returned value is valid for
all threads of its workgroup. If a task was obtained, then all threads
of the workgroup participate in the processing of the task via the
$\mathsf{process\_task}$ function (line~\ref{line:wksteal:processtask}).
Processing this task may lead to the creation of further tasks, which
the master thread will push to the workgroup's pool.
